Aldebaran~b's temperate past uncovered in planet search data

### 2018-08-03 paper/aldebaran.tex
Close #12 addressing the medalist scale in PARAM fits.
updated acknowledgments

Our new approach to asteroseismic data analysis, based on Continuous Auto-Regressive Moving Average (CARMA) models, can extract exoplanet signals together with measures of \numax from sparse and irregularly-sampled time series. An all-sky survey to find planetary companions and to precisely measure the masses of all nearby red giant stars is feasible with this new approach, and the required data either already exist in large radial velocity exoplanet surveys, or are easy to obtain with ground-based telescopes.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
TRW acknowledges the support of the Villum Foundation (research grant 10118).
D.H. acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the National Aeronautics and Space Administration under Grants NNX14AB92G and NNX17AF76G issued through the Kepler Participating Scientist Program and the K2 Guest Observer Program.

@@

\section{Stellar Modelling}\label{sec:mod}
\subsection{Stellar Models}\label{sec:stell_mod}
We used our determination of \numax and several combinations of the asteroseismic and spectroscopic parameters, along with luminosity, to estimate the fundamental stellar parameters, via fitting to stellar models. We used \textsc{MESA} models \citep{2011Paxton,2013Paxton} in conjunction with the Bayesian code \textsc{PARAM} \citep{2006dasilva, 2017Rod}.  A summary of our selected ``benchmark'' options is as follows;
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}%GUY THIS BIT COULD PROBABLY BE DROPPED AND REFERENCED OUT TO \citep{2017Rod}
\item Heavy element partitioning from \cite{1993Grevesse}.
\item OPAL equation of state \citep{2002Rogers} along with OPAL opacities \citep{1996Iglesias}, with complementary values at low temperatures from \cite{2005Ferguson}.
\item Nuclear reaction rates from NACRE \citep{1999Angulo}.
\item The atmosphere model according to \cite{1966Kris}.
\item The mixing length theory to describe convection (we adopt a solar-calibrated parameter $\alpha_{\textrm{MLT}} =1.9657$).
\item Convective overshooting on the main sequence is set to $\alpha_{\textrm{ov}}=0.2H_{p}$, with $H_{p}$ the pressure scale height at the border of the convective core. Overshooting was applied according to the \cite{1975Maeder} step function
scheme.
\item No rotational mixing or diffusion is included.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do not need to correct for the line-of-sight Doppler shift at the frequency precision available in our data \citep{2014MNRAS.445L..94D}.
\subsection{Additional modelling inputs}\label{sec:addmod}
In addition to the asteroseismic parameters, spectroscopically-determined temperature and metallicity values are needed. There exist multiple literature values for Aldebaran. We chose to compare a range of literature values to investigate what uncertainty these systematically-differing models produce in inferred stellar properties.

>>>>

Our new approach to asteroseismic data analysis, based on Continuous Auto-Regressive Moving Average (CARMA) models, can extract exoplanet signals together with measures of \numax from sparse and irregularly-sampled time series. Studies of small numbers planet-hosting giants to determine their asteroseismic parameters ordinarily require dedicated observing campaigns with hundreds or thousands of epochs \citep{2017MNRAS.472.4110S}. An all-sky survey to find planetary companions and to precisely measure the masses of all nearby red giant stars is feasible with this new approach, and the required data either already exist in large radial velocity exoplanet surveys, or are easy to obtain with ground-based telescopes.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
TRW acknowledges the support of the Villum Foundation (research grant 10118).
D.H. acknowledges support by the National Aeronautics and Space Administration under Grants NNX14AB92G, NNX17AF76G and 80NSSC18K0362 issued through the Kepler Participating Scientist Program and the K2 Guest Observer Program.

@@

\section{Stellar Modelling}\label{sec:mod}
\subsection{Stellar Models}\label{sec:stell_mod}
We used our determination of \numax and several combinations of the asteroseismic and spectroscopic parameters, along with luminosity, to estimate the fundamental stellar parameters, via fitting to stellar models. We used \textsc{MESA} models \citep{2011Paxton,2013Paxton} in conjunction with the Bayesian code \textsc{PARAM} \citep{2006dasilva, 2017Rod}.  A summary of our selected ``benchmark'' options is as follows;
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}%GUY THIS BIT COULD PROBABLY BE DROPPED AND REFERENCED OUT TO \citep{2017Rod}
\item Medalist scale from \citet{Grevesse93} as described in \citet{2017Rod}.
\item Heavy element partitioning from \cite{1993Grevesse}.
\item OPAL equation of state \citep{2002Rogers} along with OPAL opacities \citep{1996Iglesias}, with complementary values at low temperatures from \cite{2005Ferguson}.
\item Nuclear reaction rates from NACRE \citep{1999Angulo}.
\item The atmosphere model according to \cite{1966Kris}.
\item The mixing length theory to describe convection (we adopt a solar-calibrated parameter $\alpha_{\textrm{MLT}} =1.9657$).
\item Convective overshooting on the main sequence is set to $\alpha_{\textrm{ov}}=0.2H_{p}$, with $H_{p}$ the pressure scale height at the border of the convective core. Overshooting was applied according to the \cite{1975Maeder} step function
scheme.
\item No rotational mixing or diffusion is included.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do not need to correct for the line-of-sight Doppler shift at the frequency precision available in our data \citep{2014MNRAS.445L..94D}.
\subsection{Additional modelling inputs}\label{sec:addmod}
In addition to the asteroseismic parameters, spectroscopically-determined temperature and metallicity values are needed. There exist multiple literature values for Aldebaran. We chose to compare a range of literature values to investigate what uncertainty these systematically-differing models produce in inferred stellar properties.
